### 2009-08-11 doc/latex/class_cowichan_m_p_i.tex
add comment to thresh, invperc small fix

The documentation for this class was generated from the following files:\begin{CompactItemize}
\item 
cowichan\_\-mpi/\hyperlink{cowichan__mpi_8hpp}{cowichan\_\-mpi.hpp}\item 
cowichan\_\-mpi/\hyperlink{cowichan__mpi_8cpp}{cowichan\_\-mpi.cpp}\item 
cowichan\_\-mpi/\hyperlink{cowichan__mpi_2winnow_8cpp}{winnow.cpp}\end{CompactItemize}

>>>>

The documentation for this class was generated from the following files:\begin{CompactItemize}
\item 
cowichan\_\-mpi/\hyperlink{cowichan__mpi_8hpp}{cowichan\_\-mpi.hpp}\item 
cowichan\_\-mpi/\hyperlink{cowichan__mpi_8cpp}{cowichan\_\-mpi.cpp}\item 
cowichan\_\-mpi/\hyperlink{cowichan__mpi_2gauss_8cpp}{gauss.cpp}\item 
cowichan\_\-mpi/\hyperlink{cowichan__mpi_2thresh_8cpp}{thresh.cpp}\item 
cowichan\_\-mpi/\hyperlink{cowichan__mpi_2winnow_8cpp}{winnow.cpp}\end{CompactItemize}

### 2009-08-11 doc/latex/files.tex
add comment to thresh, invperc small fix

@@

>>>>

\item\contentsline{section}{cowichan\_\-mpi/\hyperlink{cowichan__mpi_2gauss_8cpp}{gauss.cpp} (MPI gauss implementation )}{\pageref{cowichan__mpi_2gauss_8cpp}}{}

@@

\item\contentsline{section}{cowichan\_\-mpi/\hyperlink{cowichan__mpi_2thresh_8cpp}{thresh.cpp} (MPI thresh implementation )}{\pageref{cowichan__mpi_2thresh_8cpp}}{}
